%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingNew}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://blog.zeerorg.site/}{\Large Rishabh Gupta}} & Email : \href{mailto:r.g.gupta@outlook.com}{r.g.gupta@outlook.com}\\
  \href{https://blog.zeerorg.site/}{blog.zeerorg.site} & Mobile : \href{tel:+919711821354}{+91-9711821354} \\
  \href{https://github.com/zeerorg}{github.com/zeerorg} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Technological University}{Delhi, India}
      {Bachelors of Technology in Computer Engineering; CGPA: 8.29}{Jul. 2015 -- Jun. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Adobe}{Noida, India}
      {Computer Scientist 1}{Feb 2023 - Present}
      \resumeItemListStart
        \resumeItem{Websocket as a service implementation}
          {Gained in-depth knowledge of the TCP, HTTP/2, and WebSocket protocol stack and led architecture discussions for websocket as a service for Adobe-wide backend teams. Championed use of Java Spring Webflux framework which led to CPU usage being reduced to half. Owned load testing for the service, achieving a 2x improvement in resource efficiency while pinpointing system bottlenecks.}
        \resumeItem{Websocket as a service prototyping}
          {Spearheaded websocket as a service prototyping, collaborating with diverse internal teams to grasp their backend integration needs. Communicated benefits of shared WebSocket connection to POCs. }
      \resumeItemListEnd
      
    \resumeSubSubheading
    {Member of Technical Staff 2}{Jul 2021 - Feb 2023}
      \resumeItemListStart
        \resumeItem{GC service}
          {Did Low Level Design of a garbage collector service deleting 90\% of unused data providing \$10,000 in savings per year alongside bringing improvements to scale and resiliency across multiple services.}
		    \resumeItem{AWS SQS to Kafka Migration}
          {Lead the efforts to develop a phased approach to ensure migration from Aws SQS based consumer to Kafka based message consumer happened with no data loss and zero disruption to millions of concurrently connected users receiving a million rpm updates.}
        \resumeItem{Alerting and Resilience}
          {Implemented Prometheus metrics integration within reporting infrastructure, resulting in cost reduction and expedited alerting mechanisms. Resolved Splunk bottleneck by architecting a custom pipeline to deliver precise calculations of monthly unique users for a high-concurrency service supporting 5 million users }
     \resumeItemListEnd


    \resumeSubheading
      {Microsoft}{Hyderabad, India}
      {Software Engineer 2}{Mar 2021 - Jul 2021}
      \resumeItemListStart
        \resumeItem{Python Load testing client}
          {Architected and did High Level Design for the first load testing approach for tasks backend written in python to shed light on the bottlenecks and do root level analysis of service behaviour, finding limits of the architecture and underlying platform.}
        \resumeItem{Getting Started Lists APIs}
          {Led the end-to-end development and implementation of the Getting Started Lists API, empowering clients to deliver a richer onboarding experience for new users, driving long-term engagement}
      \resumeItemListEnd

	  \resumeSubSubheading
		{Software Engineer 1}{Jul 2019 - Feb 2021}
		\resumeItemListStart
			\resumeItem{Tasks backend}
			{As one of the first developers of the Tasks India team I took the lead in collaborating with existing Germany based team, mastering a new codebase quickly to become a subject matter expert for the team.}
			\resumeItem{To-Do categories}
			{Directed porting of tasks categories to To-Do web removing a major blocker to adoption of the new Tasks experience in outlook web and outlook desktop partner apps, ultimately adding up over a million monthly active users.}
      % \resumeItem{Working with legacy Exchange code}
			% {This independent initiative involved deciphering the existing codebase and implementing new, efficient APIs that fueled subsequent projects like the To-Do graph API and Outlook web panel. Additionally, I fostered knowledge transfer by conducting multiple code-sharing sessions.}
		\resumeItemListEnd

	  \resumeSubSubheading
		{Software Engineer Intern}{Jun 2018 - Jul 2018}
		\resumeItemListStart
			\resumeItem{Office 365 Security}
			{Implemented multi threaded map-reduce to optimize a milion RPM read events recording and achieving multi terabyte size reduction.}
		\resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{OpenFaaS - Cron Connector}
      {Adds the ability to invoke functions based on cron expression in OpenFaas deployments.}
    \resumeSubItem{k3s in docker (k3d)}
      {A tool for helping developers working with kubernetes use a lightweight development environment.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Technologies}{: Java, C\#, JavaScript, Golang, Python, AWS, Azure, Kafka, NoSQL, Docker, Kubernetes, Redis, Spring Boot Webflux, RESTful API, Distributed Systems}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
